K2 Analysis

### 2014-04-26 text/micha_stat_analysis/notes_new.tex

To test which factors are relevant to explain the data distribution in
Table~\ref{tab:CC-ContingencyTable}, we compute log-linear models
\citep{KnokeBurke1980:Log-Linear-Mode}. The relevant factors are
\textsc{Position}, \textsc{Response}, \textsc{Condition}, and
\textsc{Accent}. As there are hardly any \emph{global} responses, we
must lump levels \emph{global} and \emph{false} of factor
\textsc{Response} into a single level \emph{other}, because otherwise
log-linear regression is not applicable. We select the ``best''
predictor of the data by a gradient search over hierarchical models in
terms of AICs. The best model takes factors \textsc{Accent},
\textsc{Response} and \textsc{Condition} into account, as well as the
interaction terms \textsc{Response:Accent} and
\textsc{Response:Condition} ($\chi^2 = 14.29$, $df=27$, $p = 0.98$,
$AIC = 32.29$ (compared to $AIC=72$ of the saturated
model)). Crucially, factor \textsc{Position} is spurious. Response
patterns only depended on the type of the sentence and whether it was
produced with accentuation.

@@

Just like for the target conditions, the best hierarchical log-linear
model (by $AIC$) includes factors \textsc{Response}, \textsc{Accent}
and \textsc{Condition}, as well as the two-way interactions
\textsc{Response:Accent} and \textsc{Response:Condition} ($\chi^2 =
23.14$, $df=42$, $p=0.99$, $AIC=47.14$ (compared to $AIC=108$ of the
saturated model)). Crucially, the observed response pattern does not
differ significantly across conditions (i.e., which reading can be
judged first), but does depend on intonational cues.

>>>>

To test which factors are relevant to explain the data distribution in
Table~\ref{tab:CC-ContingencyTable}, we compute log-linear models
\citep{KnokeBurke1980:Log-Linear-Mode}. The relevant factors are
\textsc{Position}, \textsc{Response}, \textsc{Condition}, and
\textsc{Accent}. As there are hardly any \emph{global} responses, we
must lump levels \emph{global} and \emph{false} of factor
\textsc{Response} into a single level \emph{other}, because otherwise
log-linear regression is not applicable. We select the ``best''
predictor of the data by a gradient search over hierarchical models in
terms of AICs. The best model takes factors \textsc{Accent},
\textsc{Response} and \textsc{Condition} into account, as well as the
interaction terms \textsc{Response:Accent} and
\textsc{Response:Condition} ($\chi^2 = 14.29$, $df=27$, $p = 0.98$,
$AIC = 32.29$ (compared to $AIC=72$ of the saturated
model)). Crucially, factor \textsc{Position} is spurious in the best
model. This suggests that response patterns only depend on the type of
the sentence and whether it was produced with accentuation. Moreover,
there is no interaction effect between response, accent and condition,
implying that accentuation had no relevantly different effect on
response patterns in different conditions.

@@

Just like for the target conditions, the best hierarchical log-linear
model (by $AIC$) includes factors \textsc{Response}, \textsc{Accent}
and \textsc{Condition}, as well as the two-way interactions
\textsc{Response:Accent} and \textsc{Response:Condition} ($\chi^2 =
23.14$, $df=42$, $p=0.99$, $AIC=47.14$ (compared to $AIC=108$ of the
saturated model)). Crucially, according to the best model, the
observed response pattern does not differ relevantly across positions
(i.e., which reading can be judged first), but does depend on
intonational cues. Additionally, no interaction effect between
response, accent and condition is included, suggesting that
accentuation had the same effect on response patterns in different
conditions.
